Classifying Human Driving Behavior via Deep Neural Networks

### 2017-05-18 paper/paper-DrexelFormat.tex
updated figures with latex equation

Also to simplify equation, transit matrix symbol and bias vector are skipped and vector is row vector. For example, $\vec{o} = \bold{\phi}(\vec{x}\bold{W})$ is equal to $\vec{o} = \bold{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$.

@@

\begin{enumerate}
\item Basic concepts of recurrent neural networks:

	A recurrent neural network (RNN) is a neural network that is specialized for processing a sequence of input values \cite{Goodfellow-et-al-2016}. Figure \ref{fig:RNN} illustrates abstract structure of RNN. RNN has two input. One input is from data such as normal neural network input but another input is from previous output. The property gives benefit for sequential input data. This is because past output affects to current output. With sequential data, previous data can affect to current data and RNN considers previous output for current output. It means that even input from data are equal if previous output are different, current output are also different.

@@

	To describe RNN in math equation, let $\vec{x^t} = \{ x_1^t, ..., x_n^t\} \in \mathbb{R}^n$ be a vector that represents the input data at time $t$, $\vec{h^t} = \{ h_1^t, ..., h_m^t\} \in \mathbb{R}^m$ be result from hidden layer on time $t$, and $\vec{o^t} = \{ o_1^t, ..., o_l^t\} \in \mathbb{R}^l$ be output on time $t$. For transform matrix, let $\bold{U}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for input data, $\bold{V}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be a transform matrix for data from hidden layer, and $\bold{W}: \mathbb{R}^l \rightarrow \mathbb{R}^m$ be a transform matrix for previous output. The figure \ref{fig:unfold_RNN} illustrates unfolded RNN with defined symbols. The result from hidden layer can be calculated by 
	$$\vec{h^t} = \bold{f}(\vec{x^t}\bold{U} + \vec{o^{t-1}}\bold{W} + \vec{b_h})$$ where $\bold{f}()$ is activation function for hidden layer and it is applied for each elements in given vector, $\vec{b_h} \in \mathbb{R}^m$ is a vector for hidden layer bias. Then the output can be calculated by
	$$\vec{o^t} = \bold{g}(\vec{h^t}\bold{V}+\vec{b_o})$$ where $\bold{g}()$ is activation function for output layer and it is applied for each elements in given vector, $\vec{b_o} \in \mathbb{R}^l$ is a vector for output layer bias. Therefore, RNN can be written in
	$$\vec{o^t} = \bold{g}(\bold{f}(\vec{x^t}\bold{U} + \vec{o^{t-1}}\bold{W} + \vec{b_h})\bold{V}+\vec{b_o})$$

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.5\textwidth]{pictures/figures/unfold_RNN.png}
    \caption{Unfold RNN {\color{red} change variables}}
    \label{fig:unfold_RNN}
\end{figure}

	RNN is not always like the Figure \ref{fig:unfold_RNN}. Input from previous output can be replaced by result of previous hidden layer. The main idea of RNN is when neural network decides current output it considers previous state.

\item Long Short Term Memory (LSTM) networks:

	Basic RNN has the problems of long term dependency. When RNN passes previous output for current output, some information in the input might not need or might need for future. RNN does not have ability to filter unnecessary information or to store necessary information. Long Short Term Memory (LSTM) neural network can handle these problems.

@@

		The first gate affecting to memory cells is forget gate. The forget gate decides unnecessary data from input data and previous output then applies it to memory cells. Other two gates are input gate and input modulation gate and these also affect to memory cells. The two gates decide what information remember then apply it to memory cells. The last gate is output gate and it does not directly affect to memory cells. Output gate also has two inputs from input data and previous output, and output from output gate is multiplied by memory cells to make final output. The Figure \ref{fig:LSTM} illustrates LSTM neural network with four gates and next part describes more detail of LSTM and the figure in mathematical terms.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.75\textwidth]{pictures/figures/LSTM.png}
    \caption{LSTM {\color{red} change variables}}
    \label{fig:LSTM}
\end{figure}

@@

	LSTM neural network described above is one example of LSTMs. There are many other LSTMs but all LSTMs has memory cells to store information for long term memory and has four gates: input, input modulation, forget, and output gate.
\end{enumerate}

@@

An Auto-encoder (AE) is defined as a neural network that is trained to attempt to copy its input to its output on \cite{Goodfellow-et-al-2016}. It means that AE takes input and sends it as output. However, AE does not directly send input to output. AE has two layers: encode layer and decode layer. The figure \ref{fig:AE} illustrates abstract structure of AE. Purpose of AE is to make output from decode same as input.

@@

To describe AE, let $\vec{X} = \{x_1, ..., x_n\} \in \mathbb{R}^n$ be input, $\vec{E} = \{e_1, ..., e_m\} \in \mathbb{R}^m$ be output from encoder layer, and $\vec{D} = \{d_1, ..., d_n\} \in \mathbb{R}^n$ be output of AE and output from decoder layer. For transform matrix, let $\bold{U}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for encode layer, $\bold{V}: \mathbb{R}^m \rightarrow \mathbb{R}^n$ be a transform matrix for decode layer. The figure \ref{fig:basic_AE} describes all variables defined above.

>>>>

%Also to simplify equation, transit matrix symbol and bias vector are skipped and all vector from this point is row vector. For example, $\vec{o} = \bold{\phi}(\vec{x}\bold{W})$ is equal to $\vec{o} = \bold{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$.
Also to simplify equation, transit matrix symbol is skipped and all vector from this point is row vector. For example, $\vec{o} = \bold{\phi}(\vec{x}\bold{W}+\vec{b})$ is equal to $\vec{o} = \bold{\phi}((\vec{x}^T\bold{W})^T+\vec{b})$.

@@

\subsubsection{Basic concepts of recurrent neural networks:}\label{basicRNN}
	A recurrent neural network (RNN) is a neural network that is specialized for processing a sequence of input values \cite{Goodfellow-et-al-2016}. Figure \ref{fig:RNN} illustrates abstract structure of RNN. RNN has two input. One input is from data such as normal neural network input but another input is from previous output. The property gives benefit for sequential input data. This is because past output affects to current output. With sequential data, previous data can affect to current data and RNN considers previous output for current output. It means that even input from data are equal if previous output are different, current output are also different.

@@

	To describe RNN in math equation, let $\vec{x^t} = \{ x_1^t, ..., x_n^t\} \in \mathbb{R}^n$ be a vector that represents the input data at time $t$, $\vec{h^t} = \{ h_1^t, ..., h_m^t\} \in \mathbb{R}^m$ be result from hidden layer on time $t$, and $\vec{o^t} = \{ o_1^t, ..., o_l^t\} \in \mathbb{R}^l$ be output on time $t$. For transform matrix, let $\bold{U}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for input data, $\bold{V}: \mathbb{R}^m \rightarrow \mathbb{R}^l$ be a transform matrix for data from hidden layer, and $\bold{W}: \mathbb{R}^l \rightarrow \mathbb{R}^m$ be a transform matrix for previous output. Figure \ref{fig:unfold_RNN} illustrates unfolded RNN with defined symbols. The result from hidden layer can be calculated by 
	$$\vec{h^t} = \bold{f}(\vec{x^t}\bold{U} + \vec{o^{t-1}}\bold{W} + \vec{b_h})$$ where $\bold{f}()$ is activation function for hidden layer and it is applied for each elements in given vector, $\vec{b_h} \in \mathbb{R}^m$ is a vector for hidden layer bias. Then the output can be calculated by
	$$\vec{o^t} = \bold{g}(\vec{h^t}\bold{V}+\vec{b_o})$$ where $\bold{g}()$ is activation function for output layer and it is applied for each elements in given vector, $\vec{b_o} \in \mathbb{R}^l$ is a vector for output layer bias. Therefore, RNN can be written in
	$$\vec{o^t} = \bold{g}(\bold{f}(\vec{x^t}\bold{U} + \vec{o^{t-1}}\bold{W} + \vec{b_h})\bold{V}+\vec{b_o})$$

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.65\textwidth]{pictures/figures/unfold_RNN.png}
    \caption{Unfold RNN}
    \label{fig:unfold_RNN}
\end{figure}

	RNN is not always like Figure \ref{fig:unfold_RNN}. Input from previous output can be replaced by result of previous hidden layer. The main idea of RNN is when neural network decides current output it considers previous state.

\subsubsection{Long Short Term Memory (LSTM) networks:}\label{LSTM}
	Basic RNN has the problems of long term dependency. When RNN passes previous output for current output, some information in the input might not need or might need for future. RNN does not have ability to filter unnecessary information or to store necessary information. Long Short Term Memory (LSTM) neural network can handle these problems.

@@

	The first gate affecting to memory cells is forget gate. The forget gate decides unnecessary data from input data and previous output then applies it to memory cells. Other two gates are input gate and input modulation gate and these also affect to memory cells. The two gates decide what information remember then apply it to memory cells. The last gate is output gate and it does not directly affect to memory cells. Output gate also has two inputs from input data and previous output, and output from output gate is multiplied by memory cells to make final output. Figure \ref{fig:LSTM} illustrates LSTM neural network with four gates and next part describes more detail of LSTM and the figure in mathematical terms.

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.75\textwidth]{pictures/figures/LSTM.png}
    \caption{LSTM}
    \label{fig:LSTM}
\end{figure}

@@

	LSTM neural network described above is one example of LSTMs. There are many other LSTMs but all LSTMs has memory cells to store information for long term memory and has four gates: input, input modulation, forget, and output gate.

@@

An Auto-encoder (AE) is defined as a neural network that is trained to attempt to copy its input to its output on \cite{Goodfellow-et-al-2016}. It means that AE takes input and sends it as output. However, AE does not directly send input to output. AE has two layers: encode layer and decode layer. Figure \ref{fig:AE} illustrates abstract structure of AE. Purpose of AE is to make output from decode same as input.

@@

To describe AE, let $\vec{X} = \{x_1, ..., x_n\} \in \mathbb{R}^n$ be input, $\vec{E} = \{e_1, ..., e_m\} \in \mathbb{R}^m$ be output from encoder layer, and $\vec{D} = \{d_1, ..., d_n\} \in \mathbb{R}^n$ be output of AE and output from decoder layer. For transform matrix, let $\bold{U}: \mathbb{R}^n \rightarrow \mathbb{R}^m$ be a transform matrix for encode layer, $\bold{V}: \mathbb{R}^m \rightarrow \mathbb{R}^n$ be a transform matrix for decode layer. Figure \ref{fig:basic_AE} describes all variables defined above.
